---
title: "LinearModel"
author: "Alma Andreasian"
date: "10/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
require(tidyverse)
require(tigerstats)
```

## Introduction

Form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

## SIM~Arm 1st regression

```{r}
plot(SIMS~ARM,data=data)
```

The greater the pounds of arm force(ARM), the greater the simulation(SIMS)


```{r}
cor(SIMS~ARM,data=data)
```
This number is the correlation between SIMS and ARM force. Correlation is a measure of the linear association between the two variables.


```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation is -4.095160 +  0.054563 * ARM

```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,newData, interval="prediction")
```


## SIMS~ARM regression

## SIMS~GRIP regression

## SIMS~ARM regression

## SIMS~ARM+GRIP regression

## MODEL COMPARISSON

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
